---
title: "mhtemplate"
subtitle: "A Basic Presentation Layout"
author: "Martin Haas"
date: "YYYY-MM-DD"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts, LMU_style.css]
    lib_dir: libs
    nature:
      highlightStyle: solarized-light
      highlightLines: true
      highlightSpans: true
      countIncrementalSlides: false
      ratio: "16:9"
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

class: inverse, center, middle

# Chapter Title

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=960px></html> 

---

# Title 1

## Title 2

### Title 3

---

# Lists

- Unnumbered Item 1
    - Subitem 
        - Subsubitem 
            - We have to go deeper
- Unnumbered Item 2
- Unnumbered Item 3

1. Numbered Item 1
2. Numbered Item 2
3. Numbered Item 3

---

# Table

Right Aligned | Centered   | Left Aligned
-------------:|:----------:|:------------
Cell 1        | Cell 2     | Cell 3

---

# Two-Column Style

.left-col[Left Column]

.right-col[Right Column]

---

# Code

Normal Code Block:

```{r}
mean(10)
```

Show output only with option `echo = FALSE`:

```{r echo=FALSE}
mean(10)
```


Code is not executed with option `eval = FALSE`:
```{r eval = FALSE}
mean(10)
```

Highlight code with `{{code}}`:
```{r}
{{mean(10)}}
```

---

# Text Highlighting

*Cursive* with one `*`

**Fat** with two `**`

<mark> Highlighted </mark> with `<mark>` `</mark>`




